A Machine Learning Approach to MLB Catcher Framing

### 2021-12-16 Paper.Rmd
Add references section

>>>>

A. Liaw and M. Wiener (2002). Classification and Regression by randomForest. R News 2(3), 18--22

“Baseball Savant: Trending MLB Players, Statcast and Visualizations.” Baseballsavant.com,
    https://baseballsavant.mlb.com/.

“Catcher Framing: Glossary.” MLB.com, https://www.mlb.com/glossary/statcast/catcher-framing.

Bill Petti (2021). baseballr: Functions for Acquiring and Analyzing Baseball Data.
  https://billpetti.github.io/baseballr/, https://github.com/BillPetti/baseballr/.

Brandon Greenwell, Bradley Boehmke, Jay Cunningham and GBM Developers (2020). gbm: Generalized Boosted
  Regression Models. R package version 2.1.8. https://CRAN.R-project.org/package=gbm

Jerome Friedman, Trevor Hastie, Robert Tibshirani (2010). Regularization Paths for Generalized Linear
  Models via Coordinate Descent. Journal of Statistical Software, 33(1), 1-22. URL
  https://www.jstatsoft.org/v33/i01/.

Max Kuhn (2021). caret: Classification and Regression Training. R package version 6.0-90.
  https://CRAN.R-project.org/package=caret

Wickham et al., (2019). Welcome to the tidyverse. Journal of Open Source Software, 4(43), 1686,
  https://doi.org/10.21105/joss.01686

Yihui Xie (2021). knitr: A General-Purpose Package for Dynamic Report Generation in R. R package version
  1.36.
